Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-25 paper/paper.tex
#28 expand sw22 results section

We can see in Column (1) that switching states has no immediate effect on the probability of recorded construction activity. Over the next two centuries, however, the effect grows positive and significant: 100 years after a city switches states, the probability of construction activity is 5 percentage points higher than in cities that did not switch. After 200 years this difference grows to 9 percentage points. These estimates are significant at the 5 percent and 1 percent level, respectively. Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise these dynamics.

By contrast, almost all the coefficients in Columns (2), (3) and (4) are insignificant, suggesting that neither of these specific subsets of construction is driving the results.

@@

>>>>

We can see in Column (1) that switching states has no immediate effect on the probability of recorded construction activity. Over the next two centuries, however, the effect grows positive and significant: 100 years after a city switches states, the probability of construction activity is 5 percentage points higher than in cities that did not switch. After 200 years this difference grows to 9 percentage points. These estimates are significant at the 5 percent and 1 percent level, respectively. Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise these dynamics. It looks similar to Figure BLANK, taken from \cite{schoenholzer2022}, except for the missing short-run drop. Note, however, that the outcome variable in their regression is population, which could be more sensitive to short-run effects --- after all, people may die or leave the city at an increased rate in times of political turmoil and conflict.

The regression in Column (1) used all construction activity as the outcome, while Columns (2), (3), and (4) use subsets as defined in Section \ref{sec:data}. Almost all the coefficients in the last three columns are insignificant, suggesting that neither of these specific subsets of construction is driving the results.

@@

super low within-R2
